Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-06-29 Paperfolder/Paperfolder.Rmd
updated tables done

kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.", booktabs = T, linesep = "") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
  pack_rows("Model 0", 4, 7) %>%
  pack_rows("Model 1", 8, 11) %>%
  pack_rows("Model 2", 12, 15) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", "Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1."))

```

>>>>

kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
  pack_rows("Model 0", 4, 7) %>%
  pack_rows("Model 1", 8, 11) %>%
  pack_rows("Model 2", 12, 15) %>%
    row_spec(15,  hline_after = TRUE) %>%
    pack_rows("Model 0", 17, 20) %>%
  pack_rows("Model 1", 21, 24) %>%
  pack_rows("Model 2", 25, 28) %>%
      row_spec(28,  hline_after = TRUE) %>%
  pack_rows("Model 0", 30, 33) %>%
  pack_rows("Model 1", 34, 37) %>%
  pack_rows("Model 2", 38, 41) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.")) 
```

```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
dt <- read.csv("tab/HRAFTweibF.csv", header = T)
# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")

kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
  pack_rows("Model 0", 4, 7) %>%
  pack_rows("Model 1", 8, 11) %>%
  pack_rows("Model 2", 12, 15) %>%
  row_spec(15,  hline_after = TRUE) %>%
  pack_rows("Model 0", 17, 20) %>%
  pack_rows("Model 1", 21, 24) %>%
  pack_rows("Model 2", 25, 28) %>%
  row_spec(28,  hline_after = TRUE) %>%
  pack_rows("Model 0", 30, 33) %>%
  pack_rows("Model 1", 34, 37) %>%
  pack_rows("Model 2", 38, 41) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.")) 
```
